---
output: pdf_document

---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```



# FE621.  Assignment #3.


## `r format(Sys.time(), "%Y-%m-%d")`

I pledge on my honor that I have not given or received any unauthorized assistance on this assignment/examination. I further pledge that I have not copied any material from a book, article, the Internet or any other source except where I have expressly cited the source.

Name: Tai Nguyen Cong

CWID: 10442353

# Question 1

## Question 1.1
## \textcolor{red}{Solution:} 

```{r}
# Explicit Finite Difference Method
# EU Call
explicitFDM.EC <- function(s0, k, t, r, div, sig, delx, N) {
  delt = t/N
  v = r - div - 0.5*sig^2
  
  pu = 0.5*delt*((sig/delx)^2 + v/delx)
  pm = 1 - delt*(sig/delx)^2 -r*delt
  pd = 0.5*delt*((sig/delx)^2 - v/delx)
  
  num = seq(-N, N, 1)
  stock.pr.fin = s0*exp(num*delx)
  
  EC.res = matrix(nrow = N+1, ncol = 2*N+1)
  for(i in 1:length(stock.pr.fin)) {
    EC.res[1, i] = max(c(0, stock.pr.fin[i] - k))
  }
  
  for(i in 2:(N+1)) {
    for(j in 2:(2*N)) {
      EC.res[i, j] = pd*EC.res[i-1, j-1] + pm*EC.res[i-1, j] + pu*EC.res[i-1, j+1]
      EC.res[i, 1] = EC.res[i, 2]
      EC.res[i, 2*N+1] = EC.res[i, 2*N] + stock.pr.fin[length(stock.pr.fin)] - 
        stock.pr.fin[length(stock.pr.fin)-1]
    }
  }
  return(EC.res[N+1, ceiling((2*N+1)/2)])
}

# EU Put
explicitFDM.EP <- function(s0, k, t, r, div, sig, delx, N) {
  delt = t/N
  v = r - div - 0.5*sig^2
  
  pu = 0.5*delt*((sig/delx)^2 + v/delx)
  pm = 1 - delt*(sig/delx)^2 -r*delt
  pd = 0.5*delt*((sig/delx)^2 - v/delx)
  
  num = seq(-N, N, 1)
  stock.pr.fin = s0*exp(num*delx)
  
  EP.res = matrix(nrow = N+1, ncol = 2*N+1)
  for(i in 1:length(stock.pr.fin)) {
    EP.res[1, i] = max(c(0, k - stock.pr.fin[i]))
  }
  
  for(i in 2:(N+1)) {
    for(j in 2:(2*N)) {
      EP.res[i, j] = pd*EP.res[i-1, j-1] + pm*EP.res[i-1, j] + pu*EP.res[i-1, j+1]
      EP.res[i, 2*N+1] = EP.res[i, 2*N]
      EP.res[i, 1] = EP.res[i, 2] + stock.pr.fin[2] - stock.pr.fin[1]
    }
  }
  return(EP.res[N+1, ceiling((2*N+1)/2)])
}
```


## Question 1.2
## \textcolor{red}{Solution:}

```{r}
# Implicit Finite Difference Method
# Eu Call
implicitFDM.EC<-function(s0, k, t, r, div, sig, delx, N){
  delt = t/N
  v = r - div - 0.5*sig^2
  edx = exp(delx)
  
  pu = -0.5*delt*((sig/delx)^2 + v/delx)
  pm = 1+delt*(sig/delx)^2 + r*delt
  pd = -0.5*delt*((sig/delx)^2 - v/delx)
  
  num = seq(-N, N, 1)
  stock.pr.fin = s0*exp(num*delx)
  
  lambda.u.c.eu = stock.pr.fin[length(stock.pr.fin)] - stock.pr.fin[length(stock.pr.fin)-1]
  lambda.l.c.eu = 0
  
  trid.mat <- matrix(ncol=2*N+1,nrow=2*N+1)
  trid.mat[1, ] = c(1,-1,rep(0,2*N-1))
  for(i in 2:(2*N)){
    trid.mat[i, ] = c(rep(0,i-2), pu, pm, pd, rep(0,2*N-i))
  }
  trid.mat[2*N+1, ] = c(rep(0,2*N-1), 1, -1)
  trid.mat = solve(trid.mat)
  
  EC.res = matrix(nrow = N+1, ncol = 2*N+1)
  for(i in 1:length(stock.pr.fin)) {
    EC.res[1, i] = max(c(0, stock.pr.fin[i] - k))
  }
  EC.res[1, ] = rev(EC.res[1, ])
  
  for(i in 2:(N+1)) {
    EC.res[i, ] = as.vector(trid.mat%*%
                              as.matrix( c(lambda.u.c.eu, 
                                           EC.res[i-1, ][-c(1, length(EC.res[i-1, ]))],
                                           lambda.l.c.eu), ncol = 1))
  }
  return(EC.res[N+1, ceiling((2*N+1)/2)])
}

# Eu Put
implicitFDM.EP<-function(s0, k, t, r, div, sig, delx, N){
  delt = t/N
  v = r - div - 0.5*sig^2
  edx = exp(delx)
  
  pu = -0.5*delt*((sig/delx)^2 + v/delx)
  pm = 1+delt*(sig/delx)^2 + r*delt
  pd = -0.5*delt*((sig/delx)^2 - v/delx)
  
  num = seq(-N, N, 1)
  stock.pr.fin = s0*exp(num*delx)
  
  lambda.l.c.eu = -1*(stock.pr.fin[2] - stock.pr.fin[1])
  lambda.u.c.eu = 0
  
  trid.mat <- matrix(ncol=2*N+1,nrow=2*N+1)
  trid.mat[1, ] = c(1,-1,rep(0,2*N-1))
  for(i in 2:(2*N)){
    trid.mat[i, ] = c(rep(0,i-2), pu, pm, pd, rep(0,2*N-i))
  }
  trid.mat[2*N+1, ] = c(rep(0,2*N-1), 1, -1)
  trid.mat = solve(trid.mat)
  
  EP.res = matrix(nrow = N+1, ncol = 2*N+1)
  for(i in 1:length(stock.pr.fin)) {
    EP.res[1, i] = max(c(0, k - stock.pr.fin[i]))
  }
  EP.res[1, ] = rev(EP.res[1, ])
  
  for(i in 2:(N+1)) {
    EP.res[i, ] = as.vector(trid.mat%*%
                              as.matrix( c(lambda.u.c.eu, 
                                           EP.res[i-1, ][-c(1, length(EP.res[i-1, ]))],
                                           lambda.l.c.eu), ncol = 1))
  }
  return(EP.res[N+1, ceiling((2*N+1)/2)])
}
```


## Question 1.3
## \textcolor{red}{Solution:}

```{r}
# Crank - Nicolson Finite Difference Method
# EU Call
CN.FDM.EC<-function(s0, k, t, r, div, sig, delx, N){
  delt = t/N
  v = r - div - 0.5*sig^2
  edx = exp(delx)
  
  pu = -0.25*delt*((sig/delx)^2 + v/delx)
  pm = 1 + delt*0.5*(sig/delx)^2 + 0.5*r*delt
  pd = -0.25*delt*((sig/delx)^2 - v/delx)
  
  num = seq(-N, N, 1)
  stock.pr.fin = s0*exp(num*delx)
  
  lambda.u.c.eu = stock.pr.fin[length(stock.pr.fin)] - stock.pr.fin[length(stock.pr.fin)-1]
  lambda.l.c.eu = 0
  
  trid.mat <- matrix(ncol=2*N+1,nrow=2*N+1)
  trid.mat[1, ] = c(1,-1,rep(0,2*N-1))
  for(i in 2:(2*N)){
    trid.mat[i, ] = c(rep(0,i-2), pu, pm, pd, rep(0,2*N-i))
  }
  trid.mat[2*N+1, ] = c(rep(0,2*N-1), 1, -1)
  trid.mat = solve(trid.mat)
  
  EC.res = matrix(nrow = N+1, ncol = 2*N+1)
  for(i in 1:length(stock.pr.fin)) {
    EC.res[1, i] = max(c(0, stock.pr.fin[i] - k))
  }
  EC.res[1, ] = rev(EC.res[1, ])
  
  EC.mid.mat <- matrix(nrow = N+1, ncol = 2*N+1)
  for(i in 2:(N+1)) {
    for(j in 2:(2*N)) {
      EC.mid.mat[i, j] = -1*pu*EC.res[i-1, j-1] - (pm-2)*EC.res[i-1, j] - pd*EC.res[i-1, j+1]
    }
    EC.res[i, ] = as.vector(trid.mat%*%
                              as.matrix( c(lambda.u.c.eu, 
                                           EC.mid.mat[i, ][-c(1, length(EC.mid.mat[i, ]))],
                                           lambda.l.c.eu), ncol = 1))
  }
  return(EC.res[N+1, ceiling((2*N+1)/2)])
}

# EU Put
CN.FDM.EP<-function(s0, k, t, r, div, sig, delx, N){
  delt = t/N
  v = r - div - 0.5*sig^2
  edx = exp(delx)
  
  pu = -0.25*delt*((sig/delx)^2 + v/delx)
  pm = 1 + delt*0.5*(sig/delx)^2 + 0.5*r*delt
  pd = -0.25*delt*((sig/delx)^2 - v/delx)
  
  num = seq(-N, N, 1)
  stock.pr.fin = s0*exp(num*delx)
  
  lambda.l.c.eu = -1*(stock.pr.fin[2] - stock.pr.fin[1])
  lambda.u.c.eu = 0
  
  trid.mat <- matrix(ncol=2*N+1,nrow=2*N+1)
  trid.mat[1, ] = c(1,-1,rep(0,2*N-1))
  for(i in 2:(2*N)){
    trid.mat[i, ] = c(rep(0,i-2), pu, pm, pd, rep(0,2*N-i))
  }
  trid.mat[2*N+1, ] = c(rep(0,2*N-1), 1, -1)
  trid.mat = solve(trid.mat)
  
  EP.res = matrix(nrow = N+1, ncol = 2*N+1)
  for(i in 1:length(stock.pr.fin)) {
    EP.res[1, i] = max(c(0, k - stock.pr.fin[i]))
  }
  EP.res[1, ] = rev(EP.res[1, ])
  
  EP.mid.mat <- matrix(nrow = N+1, ncol = 2*N+1)
  for(i in 2:(N+1)) {
    for(j in 2:(2*N)) {
      EP.mid.mat[i, j] = -1*pu*EP.res[i-1, j-1] - (pm-2)*EP.res[i-1, j] - pd*EP.res[i-1, j+1]
    }
    EP.res[i, ] = as.vector(trid.mat%*%
                   as.matrix( c(lambda.u.c.eu, EP.mid.mat[i, ][-c(1, length(EP.mid.mat[i, ]))],
                                           lambda.l.c.eu), ncol = 1))
  }
  return(EP.res[N+1, ceiling((2*N+1)/2)])
}
```


## Question 1.4
## \textcolor{red}{Solution:}

For all 3 methods, I choose 675 time steps for calculation, as it has been proved in the book that this should be the number of steps to choose.
```{r}
# Importing Data
s0 = 100
k = 100
t = 1
sig = 0.25
r = 0.06
div = 0.03
```

```{r}
# Applying Explicit FDM
call.explicit = explicitFDM.EC(s0, k, t, r, div, sig, 0.2, 675)
put.explicit = explicitFDM.EP(s0, k, t, r, div, sig, 0.2, 675)
# Applying Implicit FDM
call.implicit = implicitFDM.EC(s0, k, t, r, div, sig, 0.2, 675)
put.implicit = implicitFDM.EP(s0, k, t, r, div, sig, 0.2, 675)
# Applying Crank-Nicolson FDM
call.CN = CN.FDM.EC(s0, k, t, r, div, sig, 0.2, 675)
put.CN = CN.FDM.EP(s0, k, t, r, div, sig, 0.2, 675)

# Result table
call.tab.1 = matrix(c(call.explicit, call.implicit, call.CN), nrow = 1)
colnames(call.tab.1) <- c("Explicit FDM", "Implicit FDM", "Crank-Nicolson FDM")
put.tab.1 = matrix(c(put.explicit, put.implicit, put.CN), nrow = 1)
colnames(put.tab.1) <- c("Explicit FDM", "Implicit FDM", "Crank-Nicolson FDM")
call.tab.1
put.tab.1
```
We can see that in all 3 methods, the result are really simillar, which suggest that the value of call option and put option for given data are around 10.14 USD and 7.26 USD, respectively. The Explicit FDM produces a slightly higher results in both cases for call and put options.

## Question 1.5
## \textcolor{red}{Solution:}

In this part, I choose time step equals 1/3 so that we can see clearly how Pu, Pm, Pd would diverge. If I choose large number of steps (i.e small time step) then it would create parallel lines.
```{r}
library(ggplot2)
delx.a = 0.2
delt.a = 1/3

sig.seq =seq(0.05, 0.6, 0.05)
v.seq = r - div - 0.5*sig.seq^2
pu.implicit = -0.5*delt.a*((sig.seq/delx.a)^2 + v.seq/delx.a)
pm.implicit = 1+delt.a*(sig.seq/delx.a)^2 + r*delt.a
pd.implicit = -0.5*delt.a*((sig.seq/delx.a)^2 - v.seq/delx.a)
df <- data.frame(x=c(pu.implicit, pm.implicit, pd.implicit), val=sig.seq, 
                 variable=c(rep("Pu", length(sig.seq)), 
                            rep("Pm", length(sig.seq)), rep("Pd", length(sig.seq)) ))
# plot
p <- ggplot(data = df, aes(x=val, y=x)) + geom_line(aes(colour=variable))
p + xlab("Volatility") + ylab("Values of Pu, Pm, Pd") + ggtitle("Change of Coefficients")
```
From the plot, we can see that, as we increase the value of $\sigma$, the values for Pu, Pm and Pd seems to diverge. Specifically, as $\sigma$ increases, Pm tends to become larger, while Pu and Pd tends to converge together to the very small and negative amounts. This is because for the formula for Pu, Pm, Pd, we can see that coefficient for $\sigma$ in Pm is positive, while those are negative for Pu and Pd, so when we increase $\sigma$, the result as in the plot occured.

## Question 1.6
## \textcolor{red}{Solution:}

```{r}
#  Function computing Greeks of Call option
explicitFDM.EC.Greeks <- function(s0, k, t, r, div, sig, delx, N) {
  delt = t/N
  v = r - div - 0.5*sig^2
  
  pu = 0.5*delt*((sig/delx)^2 + v/delx)
  pm = 1 - delt*(sig/delx)^2 -r*delt
  pd = 0.5*delt*((sig/delx)^2 - v/delx)
  
  num = seq(-N, N, 1)
  stock.pr.fin = s0*exp(num*delx)
  
  EC.res = matrix(nrow = N+1, ncol = 2*N+1)
  for(i in 1:length(stock.pr.fin)) {
    EC.res[1, i] = max(c(0, stock.pr.fin[i] - k))
  }
  
  for(i in 2:(N+1)) {
    for(j in 2:(2*N)) {
      EC.res[i, j] = pd*EC.res[i-1, j-1] + pm*EC.res[i-1, j] + pu*EC.res[i-1, j+1]
      EC.res[i, 1] = EC.res[i, 2]
      EC.res[i, 2*N+1] = EC.res[i, 2*N] + stock.pr.fin[length(stock.pr.fin)] - 
        stock.pr.fin[length(stock.pr.fin)-1]
    }
  }
  
  delta = (EC.res[N+1, ceiling((2*N+1)/2)+1] - EC.res[N+1, ceiling((2*N+1)/2)-1])/
    (stock.pr.fin[ceiling((2*N+1)/2)+1] - stock.pr.fin[ceiling((2*N+1)/2)-1])
  
  gamma = ((EC.res[N+1, ceiling((2*N+1)/2)+1] - EC.res[N+1, ceiling((2*N+1)/2)])/
    (stock.pr.fin[ceiling((2*N+1)/2)+1] - stock.pr.fin[ceiling((2*N+1)/2)]) - 
    (EC.res[N+1, ceiling((2*N+1)/2)] - EC.res[N+1, ceiling((2*N+1)/2)-1])/
    (stock.pr.fin[ceiling((2*N+1)/2)] - stock.pr.fin[ceiling((2*N+1)/2)-1]))/
    (0.5*stock.pr.fin[ceiling((2*N+1)/2)+1] - 0.5*stock.pr.fin[ceiling((2*N+1)/2)-1])
  
  theta = (EC.res[N, ceiling((2*N+1)/2)+1] - EC.res[N+1, ceiling((2*N+1)/2)+1])/delt
  
  vega = (explicitFDM.EC(s0, k, t, r, div, sig*1.001, delx, N) - 
    explicitFDM.EC(s0, k, t, r, div, sig*0.999, delx, N))/(2*0.001*sig)
  
  greeks.res <- matrix(c(delta, gamma, theta, vega), nrow = 1)
  colnames(greeks.res) <- c("Delta", "Gamma", "Theta", "Vega")
  return(greeks.res)
}

#  Function computing Greeks of Put option
explicitFDM.EP.Greeks <- function(s0, k, t, r, div, sig, delx, N) {
  delt = t/N
  v = r - div - 0.5*sig^2
  
  pu = 0.5*delt*((sig/delx)^2 + v/delx)
  pm = 1 - delt*(sig/delx)^2 -r*delt
  pd = 0.5*delt*((sig/delx)^2 - v/delx)
  
  num = seq(-N, N, 1)
  stock.pr.fin = s0*exp(num*delx)
  
  EP.res = matrix(nrow = N+1, ncol = 2*N+1)
  for(i in 1:length(stock.pr.fin)) {
    EP.res[1, i] = max(c(0, k - stock.pr.fin[i]))
  }
  
  for(i in 2:(N+1)) {
    for(j in 2:(2*N)) {
      EP.res[i, j] = pd*EP.res[i-1, j-1] + pm*EP.res[i-1, j] + pu*EP.res[i-1, j+1]
      EP.res[i, 2*N+1] = EP.res[i, 2*N]
      EP.res[i, 1] = EP.res[i, 2] + stock.pr.fin[2] - stock.pr.fin[1]
    }
  }
  
  delta = (EP.res[N+1, ceiling((2*N+1)/2)+1] - EP.res[N+1, ceiling((2*N+1)/2)-1])/
    (stock.pr.fin[ceiling((2*N+1)/2)+1] - stock.pr.fin[ceiling((2*N+1)/2)-1])
  
  gamma = ((EP.res[N+1, ceiling((2*N+1)/2)+1] - EP.res[N+1, ceiling((2*N+1)/2)])/
             (stock.pr.fin[ceiling((2*N+1)/2)+1] - stock.pr.fin[ceiling((2*N+1)/2)]) - 
             (EP.res[N+1, ceiling((2*N+1)/2)] - EP.res[N+1, ceiling((2*N+1)/2)-1])/
             (stock.pr.fin[ceiling((2*N+1)/2)] - stock.pr.fin[ceiling((2*N+1)/2)-1]))/
    (0.5*stock.pr.fin[ceiling((2*N+1)/2)+1] - 0.5*stock.pr.fin[ceiling((2*N+1)/2)-1])
  
  theta = (EP.res[N, ceiling((2*N+1)/2)+1] - EP.res[N+1, ceiling((2*N+1)/2)+1])/delt
  
  vega = (explicitFDM.EP(s0, k, t, r, div, sig*1.001, delx, N) - 
            explicitFDM.EP(s0, k, t, r, div, sig*0.999, delx, N))/(2*0.001*sig)
  
  greeks.res <- matrix(c(delta, gamma, theta, vega), nrow = 1)
  colnames(greeks.res) <- c("Delta", "Gamma", "Theta", "Vega")
  return(greeks.res)
}
```

```{r}
# Greeks of Call option
explicitFDM.EC.Greeks(s0, k, t, r, div, sig, 0.2, 675)
# Greeks of Put option
explicitFDM.EP.Greeks(s0, k, t, r, div, sig, 0.2, 675)
```
The result for Greeks of call and put options are presented in 2 tables above.


# Question 2

## Question 2.1
## \textcolor{red}{Solution:}

```{r}
library(quantmod)

# Getting Data function
get.data.FDM <- function(ticker, start.date, end.date, 
                        exp.date1, exp.date2, exp.date3) {
  secp <- getSymbols(Symbols = as.character(ticker), from = start.date, 
                     to = end.date, auto.assign = F, src = 'yahoo')
  optd1 <- getOptionChain(as.character(ticker), auto.assign = F, 
                          exp.date1, src = 'yahoo')
  optd2 <- getOptionChain(as.character(ticker), auto.assign = F,
                          exp.date2, src = 'yahoo')
  optd3 <- getOptionChain(as.character(ticker), auto.assign = F,
                          exp.date3, src = 'yahoo')
  
  c1 <- data.frame(optd1$calls)
  colnames(c1) <- c(paste(c(ticker), "Call.1m.Strike", sep = "."), 
                    paste(c(ticker), "Call.1m.Last", sep = "."), 
                    paste(c(ticker), "Call.1m.Chg", sep = "."), 
                    paste(c(ticker), "Call.1m.Bid", sep = "."),
                    paste(c(ticker), "Call.1m.Ask", sep = "."), 
                    paste(c(ticker), "Call.1m.Vol", sep = "."), 
                    paste(c(ticker), "Call.1m.OI", sep = "."))
  p1 <- data.frame(optd1$puts)
  colnames(p1) <- c(paste(c(ticker), "Put.1m.Strike", sep = "."), 
                    paste(c(ticker), "Put.1m.Last", sep = "."), 
                    paste(c(ticker), "Put.1m.Chg", sep = "."), 
                    paste(c(ticker), "Put.1m.Bid", sep = "."),
                    paste(c(ticker), "Put.1m.Ask", sep = "."), 
                    paste(c(ticker), "Put.1m.Vol", sep = "."), 
                    paste(c(ticker), "Put.1m.OI", sep = "."))
  
  c2 <- data.frame(optd2$calls)
  colnames(c2) <- c(paste(c(ticker), "Call.2m.Strike", sep = "."), 
                    paste(c(ticker), "Call.2m.Last", sep = "."), 
                    paste(c(ticker), "Call.2m.Chg", sep = "."), 
                    paste(c(ticker), "Call.2m.Bid", sep = "."),
                    paste(c(ticker), "Call.2m.Ask", sep = "."), 
                    paste(c(ticker), "Call.2m.Vol", sep = "."), 
                    paste(c(ticker), "Call.2m.OI", sep = "."))
  p2 <- data.frame(optd2$puts)
  colnames(p2) <- c(paste(c(ticker), "Put.2m.Strike", sep = "."), 
                    paste(c(ticker), "Put.2m.Last", sep = "."), 
                    paste(c(ticker), "Put.2m.Chg", sep = "."), 
                    paste(c(ticker), "Put.2m.Bid", sep = "."),
                    paste(c(ticker), "Put.2m.Ask", sep = "."), 
                    paste(c(ticker), "Put.2m.Vol", sep = "."), 
                    paste(c(ticker), "Put.2m.OI", sep = "."))
  
  c3 <- data.frame(optd3$calls)
  colnames(c3) <- c(paste(c(ticker), "Call.3m.Strike", sep = "."), 
                    paste(c(ticker), "Call.3m.Last", sep = "."), 
                    paste(c(ticker), "Call.3m.Chg", sep = "."), 
                    paste(c(ticker), "Call.3m.Bid", sep = "."),
                    paste(c(ticker), "Call.3m.Ask", sep = "."), 
                    paste(c(ticker), "Call.3m.Vol", sep = "."), 
                    paste(c(ticker), "Call.3m.OI", sep = "."))
  p3 <- data.frame(optd3$puts)
  colnames(p3) <- c(paste(c(ticker), "Put.3m.Strike", sep = "."), 
                    paste(c(ticker), "Put.3m.Last", sep = "."), 
                    paste(c(ticker), "Put.3m.Chg", sep = "."), 
                    paste(c(ticker), "Put.3m.Bid", sep = "."),
                    paste(c(ticker), "Put.3m.Ask", sep = "."), 
                    paste(c(ticker), "Put.3m.Vol", sep = "."), 
                    paste(c(ticker), "Put.3m.OI", sep = "."))
  secp <- data.frame(secp)
  all.dat <- c(secp, c1, p1, c2, p2, c3, p3)
  return(all.dat)
}
```

Implied volatility functions for put and call options.
```{r}
# Implied volatility
# Using Newton Method
# Call
CallBSIMPVol <- function(spot.price, time.to.maturity, risk.free, strike.price, 
                         option.price, initial.guess) {
  
  fx <-  function(sig){
    d1 <- (log(spot.price/strike.price) + (risk.free + sig^2 * 0.5) * time.to.maturity) / 
      (sig * sqrt(time.to.maturity))
    d2 <- d1 - sig * sqrt(time.to.maturity)
    value <- spot.price * pnorm(d1) - strike.price * exp( -risk.free * time.to.maturity) * 
      pnorm(d2) - option.price
    return(value)
  }
  
  dfx <- function(sig){
    d1 <- (log(spot.price/strike.price) + (risk.free + sig^2 * 0.5) * time.to.maturity) /
      (sig*sqrt(time.to.maturity))
    d2 <- d1 - sig * sqrt(time.to.maturity)
    value <- strike.price * exp( -risk.free * time.to.maturity) * dnorm(d2) * 
      sqrt(time.to.maturity)
    return(value)
  }
  
  q1 <- function(x0){
    epsilon <- 0.5
    while(T){
      tmp <-  x0
      deltaX  <-  fx(x0)/dfx(x0)
      x0  <-  x0 - deltaX
      if (abs(x0-tmp) < epsilon){
        
        break  
      }else {
        print(x0)
      }
    }
    return(x0)
  }
  
  IMPvol <- q1(initial.guess)
  return(IMPvol)
}

# Put
PutBSIMPVol <- function(spot.price, time.to.maturity, risk.free, strike.price, 
                        option.price, initial.guess) {
  
  fx <-  function(sig){
    d1 <- (log(spot.price/strike.price) + (risk.free + sig^2 * 0.5) * time.to.maturity) / 
      (sig * sqrt(time.to.maturity))
    d2 <- d1 - sig * sqrt(time.to.maturity)
    value <- pnorm(-d2) * strike.price * exp(-risk.free * time.to.maturity) - pnorm(-d1) * 
      spot.price - option.price
    return(value)
  }
  
  dfx <- function(sig){
    d1 <- (log(spot.price/strike.price) + (risk.free + sig^2 * 0.5) * time.to.maturity) / 
      (sig*sqrt(time.to.maturity))
    d2 <- d1 - sig * sqrt(time.to.maturity)
    value <- strike.price * exp( -risk.free * time.to.maturity) * dnorm(-d2) * 
      sqrt(time.to.maturity)
    return(value)
  }
  
  q1 <- function(x0){
    epsilon <- 0.5
    while(T){
      tmp <-  x0
      deltaX  <-  fx(x0)/dfx(x0)
      x0  <-  x0 - deltaX
      if (abs(x0-tmp) < epsilon){
        
        break  
      }else {
        
      }
    }
    return(x0)
  }
  
  IMPvol <- q1(initial.guess)
  return(IMPvol)
}
```

Here, I use the federal fund rate of the 22nd October, 2019. I choose 10 strike price that are closest to the spot price of the stock, by considering the difference to see which ones are closest and choose them.
```{r}
AMZN.FDM <- get.data.FDM("AMZN", "2019-10-22", "2019-10-23", "2019-11-22", 
                         "2019-12-20", "2020-01-17")
amzn.fdm.sp = AMZN.FDM$AMZN.Adjusted
r.fdm <- 0.0185 # 22 Oct

which.min(abs(AMZN.FDM$AMZN.Adjusted - AMZN.FDM$AMZN.Call.1m.Strike))
which.min(abs(AMZN.FDM$AMZN.Adjusted - AMZN.FDM$AMZN.Call.2m.Strike))
which.min(abs(AMZN.FDM$AMZN.Adjusted - AMZN.FDM$AMZN.Call.3m.Strike))

which.min(abs(AMZN.FDM$AMZN.Adjusted - AMZN.FDM$AMZN.Put.1m.Strike))
which.min(abs(AMZN.FDM$AMZN.Adjusted - AMZN.FDM$AMZN.Put.2m.Strike))
which.min(abs(AMZN.FDM$AMZN.Adjusted - AMZN.FDM$AMZN.Put.3m.Strike))

amzn.fdm.call.1m.strike = AMZN.FDM$AMZN.Call.1m.Strike[45:54]
amzn.fdm.call.2m.strike = AMZN.FDM$AMZN.Call.2m.Strike[46:55]
amzn.fdm.call.3m.strike = AMZN.FDM$AMZN.Call.3m.Strike[109:118]

amzn.fdm.put.1m.strike = AMZN.FDM$AMZN.Put.1m.Strike[101:110]
amzn.fdm.put.2m.strike = AMZN.FDM$AMZN.Put.2m.Strike[68:77]
amzn.fdm.put.3m.strike = AMZN.FDM$AMZN.Put.3m.Strike[109:118]

# Calculating options price to compute volatility
amzn.fdm.call.option.price.1m <- c()
amzn.fdm.call.option.price.2m <- c()
amzn.fdm.call.option.price.3m <- c()
amzn.fdm.put.option.price.1m <- c()
amzn.fdm.put.option.price.2m <- c()
amzn.fdm.put.option.price.3m <- c()
for(i in 1:10) {
  amzn.fdm.call.option.price.1m[i] = (AMZN.FDM$AMZN.Call.1m.Ask[i+44] + 
                                        AMZN.FDM$AMZN.Call.1m.Bid[i+44])/2
  amzn.fdm.call.option.price.2m[i] = (AMZN.FDM$AMZN.Call.2m.Ask[i+45] + 
                                        AMZN.FDM$AMZN.Call.2m.Bid[i+45])/2
  amzn.fdm.call.option.price.3m[i] = (AMZN.FDM$AMZN.Call.3m.Ask[i+108] + 
                                        AMZN.FDM$AMZN.Call.3m.Bid[i+108])/2
  amzn.fdm.put.option.price.1m[i] = (AMZN.FDM$AMZN.Put.1m.Ask[i+100] + 
                                       AMZN.FDM$AMZN.Put.1m.Bid[i+100])/2
  amzn.fdm.put.option.price.2m[i] = (AMZN.FDM$AMZN.Put.2m.Ask[i+67] + 
                                       AMZN.FDM$AMZN.Put.2m.Bid[i+67])/2
  amzn.fdm.put.option.price.3m[i] = (AMZN.FDM$AMZN.Put.3m.Ask[i+108] + 
                                       AMZN.FDM$AMZN.Put.3m.Bid[i+108])/2
}

t1 = 31/365
t2 = 59/365
t3 = 87/365

# Computing volatility
amzn.fdm.vol.c1 <- c()
amzn.fdm.vol.c2 <- c()
amzn.fdm.vol.c3 <- c()
amzn.fdm.vol.p1 <- c()
amzn.fdm.vol.p2 <- c()
amzn.fdm.vol.p3 <- c()
for(i in 1:10) {
  amzn.fdm.vol.c1[i] = CallBSIMPVol(amzn.fdm.sp, t1, r.fdm, amzn.fdm.call.1m.strike[i], 
                                    amzn.fdm.call.option.price.1m[i], 0.5)
  amzn.fdm.vol.c2[i] = CallBSIMPVol(amzn.fdm.sp, t2, r.fdm, amzn.fdm.call.2m.strike[i], 
                                    amzn.fdm.call.option.price.2m[i], 0.5)
  amzn.fdm.vol.c3[i] = CallBSIMPVol(amzn.fdm.sp, t3, r.fdm, amzn.fdm.call.3m.strike[i], 
                                    amzn.fdm.call.option.price.3m[i], 0.5)
  amzn.fdm.vol.p1[i] = PutBSIMPVol(amzn.fdm.sp, t1, r.fdm, amzn.fdm.put.1m.strike[i], 
                                   amzn.fdm.put.option.price.1m[i], 0.5)
  amzn.fdm.vol.p2[i] = PutBSIMPVol(amzn.fdm.sp, t2, r.fdm, amzn.fdm.put.2m.strike[i], 
                                   amzn.fdm.put.option.price.2m[i], 0.5)
  amzn.fdm.vol.p3[i] = PutBSIMPVol(amzn.fdm.sp, t3, r.fdm, amzn.fdm.put.3m.strike[i], 
                                     amzn.fdm.put.option.price.3m[i], 0.5)
}
```

## Question 2.2
## \textcolor{red}{Solution:}

Since the implied volatility for the same terms (1, 2 and 3 months) of different strike prices are very close, so I can choose 1 value of space step for each terms of all 10 strike prices. For 1 month, I choose $\Delta x$ = 0.02, for 2 months, $\Delta x$ = 0.025 and for 3 months, $\Delta x$ = 0.027. Also, I use 675 time steps as in Problem 1 for calculation.
```{r}
# Computing price of options using FDMs implemented above
explicit.price.call.1m.pred <- c()
explicit.price.call.2m.pred <- c()
explicit.price.call.3m.pred <- c()
explicit.price.put.1m.pred <- c()
explicit.price.put.2m.pred <- c()
explicit.price.put.3m.pred <- c()

implicit.price.call.1m.pred <- c()
implicit.price.call.2m.pred <- c()
implicit.price.call.3m.pred <- c()
implicit.price.put.1m.pred <- c()
implicit.price.put.2m.pred <- c()
implicit.price.put.3m.pred <- c()

CN.price.call.1m.pred <- c()
CN.price.call.2m.pred <- c()
CN.price.call.3m.pred <- c()
CN.price.put.1m.pred <- c()
CN.price.put.2m.pred <- c()
CN.price.put.3m.pred <- c()

for(i in 1:10) {
  explicit.price.call.1m.pred[i] = explicitFDM.EC(amzn.fdm.sp, amzn.fdm.call.1m.strike[i], 
                                                  t1, r.fdm, 0, amzn.fdm.vol.c1[i], 0.02, 675)
  explicit.price.call.2m.pred[i] = explicitFDM.EC(amzn.fdm.sp, amzn.fdm.call.2m.strike[i], 
                                                  t2, r.fdm, 0, amzn.fdm.vol.c2[i], 0.025, 675)
  explicit.price.call.3m.pred[i] = explicitFDM.EC(amzn.fdm.sp, amzn.fdm.call.3m.strike[i], 
                                                  t3, r.fdm, 0, amzn.fdm.vol.c3[i], 0.027, 675)
  explicit.price.put.1m.pred[i] = explicitFDM.EP(amzn.fdm.sp, amzn.fdm.put.1m.strike[i], 
                                                 t1, r.fdm, 0, amzn.fdm.vol.p1[i], 0.02, 675)
  explicit.price.put.2m.pred[i] = explicitFDM.EP(amzn.fdm.sp, amzn.fdm.put.2m.strike[i], 
                                                 t2, r.fdm, 0, amzn.fdm.vol.p2[i], 0.025, 675)
  explicit.price.put.3m.pred[i] = explicitFDM.EP(amzn.fdm.sp, amzn.fdm.put.3m.strike[i], 
                                                 t3, r.fdm, 0, amzn.fdm.vol.p3[i], 0.027, 675)
  
  implicit.price.call.1m.pred[i] = implicitFDM.EC(amzn.fdm.sp, amzn.fdm.call.1m.strike[i], 
                                                  t1, r.fdm, 0, amzn.fdm.vol.c1[i], 0.02, 675)
  implicit.price.call.2m.pred[i] = implicitFDM.EC(amzn.fdm.sp, amzn.fdm.call.2m.strike[i], 
                                                  t2, r.fdm, 0, amzn.fdm.vol.c2[i], 0.025, 675)
  implicit.price.call.3m.pred[i] = implicitFDM.EC(amzn.fdm.sp, amzn.fdm.call.3m.strike[i], 
                                                  t3, r.fdm, 0, amzn.fdm.vol.c3[i], 0.027, 675)
  implicit.price.put.1m.pred[i] = implicitFDM.EP(amzn.fdm.sp, amzn.fdm.put.1m.strike[i], 
                                                 t1, r.fdm, 0, amzn.fdm.vol.p1[i], 0.02, 675)
  implicit.price.put.2m.pred[i] = implicitFDM.EP(amzn.fdm.sp, amzn.fdm.put.2m.strike[i], 
                                                 t2, r.fdm, 0, amzn.fdm.vol.p2[i], 0.025, 675)
  implicit.price.put.3m.pred[i] = implicitFDM.EP(amzn.fdm.sp, amzn.fdm.put.3m.strike[i], 
                                                 t3, r.fdm, 0, amzn.fdm.vol.p3[i], 0.027, 675)
  
  CN.price.call.1m.pred[i] = CN.FDM.EC(amzn.fdm.sp, amzn.fdm.call.1m.strike[i], 
                                       t1, r.fdm, 0, amzn.fdm.vol.c1[i], 0.02, 675)
  CN.price.call.2m.pred[i] = CN.FDM.EC(amzn.fdm.sp, amzn.fdm.call.2m.strike[i], 
                                       t2, r.fdm, 0, amzn.fdm.vol.c2[i], 0.025, 675)
  CN.price.call.3m.pred[i] = CN.FDM.EC(amzn.fdm.sp, amzn.fdm.call.3m.strike[i], 
                                       t3, r.fdm, 0, amzn.fdm.vol.c3[i], 0.027, 675)
  CN.price.put.1m.pred[i] = CN.FDM.EP(amzn.fdm.sp, amzn.fdm.put.1m.strike[i], 
                                      t1, r.fdm, 0, amzn.fdm.vol.p1[i], 0.02, 675)
  CN.price.put.2m.pred[i] = CN.FDM.EP(amzn.fdm.sp, amzn.fdm.put.2m.strike[i], 
                                      t2, r.fdm, 0, amzn.fdm.vol.p2[i], 0.025, 675)
  CN.price.put.3m.pred[i] = CN.FDM.EP(amzn.fdm.sp, amzn.fdm.put.3m.strike[i], 
                                      t3, r.fdm, 0, amzn.fdm.vol.p3[i], 0.027, 675)
}
```

```{r}
# Result table
FDM.call.tab.1m <- matrix(c(explicit.price.call.1m.pred, implicit.price.call.1m.pred, 
                          CN.price.call.1m.pred, amzn.fdm.call.option.price.1m), 
                          ncol = 10, byrow = T)
colnames(FDM.call.tab.1m) <- c(as.character(amzn.fdm.call.1m.strike))
rownames(FDM.call.tab.1m) <- c("Explicit FDM", "Implicit FDM", "Crank Nicolson FDM", 
                               "(Bid + Ask)/2")
FDM.call.tab.1m

FDM.call.tab.2m <- matrix(c(explicit.price.call.2m.pred, implicit.price.call.2m.pred, 
                            CN.price.call.2m.pred, amzn.fdm.call.option.price.2m),
                          ncol = 10, byrow = T)
colnames(FDM.call.tab.2m) <- c(as.character(amzn.fdm.call.2m.strike))
rownames(FDM.call.tab.2m) <- c("Explicit FDM", "Implicit FDM", "Crank Nicolson FDM", 
                               "(Bid + Ask)/2")
FDM.call.tab.2m

FDM.call.tab.3m <- matrix(c(explicit.price.call.3m.pred, implicit.price.call.3m.pred, 
                            CN.price.call.3m.pred, amzn.fdm.call.option.price.3m), 
                          ncol = 10, byrow = T)
colnames(FDM.call.tab.3m) <- c(as.character(amzn.fdm.call.3m.strike))
rownames(FDM.call.tab.3m) <- c("Explicit FDM", "Implicit FDM", "Crank Nicolson FDM", 
                               "(Bid + Ask)/2")
FDM.call.tab.3m

FDM.put.tab.1m <- matrix(c(explicit.price.put.1m.pred, implicit.price.put.1m.pred, 
                            CN.price.put.1m.pred, amzn.fdm.put.option.price.1m), 
                         ncol = 10, byrow = T)
colnames(FDM.put.tab.1m) <- c(as.character(amzn.fdm.put.1m.strike))
rownames(FDM.put.tab.1m) <- c("Explicit FDM", "Implicit FDM", "Crank Nicolson FDM", 
                              "(Bid + Ask)/2")
FDM.put.tab.1m

FDM.put.tab.2m <- matrix(c(explicit.price.put.2m.pred, implicit.price.put.2m.pred, 
                           CN.price.put.2m.pred, amzn.fdm.put.option.price.2m), 
                         ncol = 10, byrow = T)
colnames(FDM.put.tab.2m) <- c(as.character(amzn.fdm.put.2m.strike))
rownames(FDM.put.tab.2m) <- c("Explicit FDM", "Implicit FDM", "Crank Nicolson FDM", 
                              "(Bid + Ask)/2")
FDM.put.tab.2m

FDM.put.tab.3m <- matrix(c(explicit.price.put.3m.pred, implicit.price.put.3m.pred, 
                           CN.price.put.3m.pred, amzn.fdm.put.option.price.3m), 
                         ncol = 10, byrow = T)
colnames(FDM.put.tab.3m) <- c(as.character(amzn.fdm.put.3m.strike))
rownames(FDM.put.tab.3m) <- c("Explicit FDM", "Implicit FDM", "Crank Nicolson FDM", 
                              "(Bid + Ask)/2")
FDM.put.tab.3m
```
All result produces result roughly the same as the real options prices, especially for options with large strike prices.

## Question 2.3
## \textcolor{red}{Solution:}

```{r}
call.greeks.1m <- vector("list", 10)
call.greeks.2m <- vector("list", 10)
call.greeks.3m <- vector("list", 10)
put.greeks.1m <- vector("list", 10)
put.greeks.2m <- vector("list", 10)
put.greeks.3m <- vector("list", 10)

for(i in 1:10) {
  call.greeks.1m[[i]] = explicitFDM.EC.Greeks(amzn.fdm.sp, amzn.fdm.call.1m.strike[i], 
                                              t1, r.fdm, 0, amzn.fdm.vol.c1[i], 0.02, 675)
  call.greeks.2m[[i]] = explicitFDM.EC.Greeks(amzn.fdm.sp, amzn.fdm.call.2m.strike[i], 
                                              t2, r.fdm, 0, amzn.fdm.vol.c2[i], 0.025, 675)
  call.greeks.3m[[i]] = explicitFDM.EC.Greeks(amzn.fdm.sp, amzn.fdm.call.3m.strike[i], 
                                              t3, r.fdm, 0, amzn.fdm.vol.c3[i], 0.027, 675)
  put.greeks.1m[[i]] = explicitFDM.EP.Greeks(amzn.fdm.sp, amzn.fdm.put.1m.strike[i], 
                                             t1, r.fdm, 0, amzn.fdm.vol.p1[i], 0.02, 675)
  put.greeks.2m[[i]] = explicitFDM.EP.Greeks(amzn.fdm.sp, amzn.fdm.put.2m.strike[i], 
                                             t2, r.fdm, 0, amzn.fdm.vol.p2[i], 0.025, 675)
  put.greeks.3m[[i]] = explicitFDM.EP.Greeks(amzn.fdm.sp, amzn.fdm.put.3m.strike[i], 
                                             t3, r.fdm, 0, amzn.fdm.vol.p3[i], 0.027, 675)
}

names(call.greeks.1m) <- amzn.fdm.call.1m.strike
names(call.greeks.2m) <- amzn.fdm.call.2m.strike
names(call.greeks.3m) <- amzn.fdm.call.3m.strike
names(put.greeks.1m) <- amzn.fdm.put.1m.strike
names(put.greeks.2m) <- amzn.fdm.put.2m.strike
names(put.greeks.3m) <- amzn.fdm.put.3m.strike
```

```{r}
call.greeks.1m
call.greeks.2m
call.greeks.3m
put.greeks.1m
put.greeks.2m
put.greeks.3m
```
The results for Greeks of call and put options with different strike prices as presented in tables above. We can see baisc properties of Greeks, such as Delta of call options are always positive, while those are always negative for put options, or Vega of the same strike price for call and put options are the same. In the case above, Vega of same strike prices are roughly the same.


# Question 3
## \textcolor{red}{Solution:}

For this problem, I use the grid of 50 possible values for stock price and 40 possible values for implied volatility at the maturity. At maturity, stock prices ranges from 0 to 2 times value of stock prices and volatility range from 0 to 1.8 time values of implied volaatility. I also use 2000 time steps for calculation. After the 2000th time steps, I got a matrix of possible values for options at the beginning. This is the 2 dimensions matrix of the corresponding stock price and volatility, hence I use 2 dimensional interpolation to get the value of options with given data.
```{r}
library(pracma)
s0 = 100
K = 100
t = 1
r = 0.06
v0 = 0.0625
kappa = 2
theta = 0.09
sig = 0.5
rho = 0.6

# Computing range of stock price, volatility, ds, dt, dv
s.vec <- seq(0, 2*s0, length.out = 50)
sig.vec <- seq(0, 1.8*sig, length.out = 40)
NS = length(s.vec)
NV = length(sig.vec)
NT = 2000

ds = (s.vec[length(s.vec)] - s.vec[1])/NS
dv = (sig.vec[length(sig.vec)] - sig.vec[1])/NV
dt = t/NT

# Initializing price data as an array of 3 dimensions
price.array <- array(data = NA, dim = c(NS, NV, NT+1))
for(s in 1:NS) {
  price.array[s, , 1] = max(0 , K - s.vec[s])
}

# Initializing array containing values for coefficients of previous 
# time step to compute value of options
A <- array(data = NA, dim = c(NS, NV, NT+1))
B <- array(data = NA, dim = c(NS, NV, NT+1))
C <- array(data = NA, dim = c(NS, NV, NT+1))
D <- array(data = NA, dim = c(NS, NV, NT+1))
E <- array(data = NA, dim = c(NS, NV, NT+1))
G <- array(data = NA, dim = c(NS, NV, NT+1))
for(t in 1:(NT+1)) {
  for(s in 1:NS) {
    for(v in 1:NV) {
      A[1, v, t] = 0; B[1, v, t] = 0; C[1, v, t] = 0
      D[1, v, t] = 0; E[1, v, t] = 0; G[1, v, t] = 0
      
      A[NS, v, t] = 0; B[NS, v, t] = 0; C[NS, v, t] = 0
      D[NS, v, t] = 0; E[NS, v, t] = 0; G[NS, v, t] = 0
      
      A[s, 1, t] = 0; B[s, 1, t] = 0; C[s, 1, t] = 0
      D[s, 1, t] = 0; E[s, 1, t] = 0; G[s, 1, t] = 0
      
      A[s, NV, t] = 0; B[s, NV, t] = 0; C[s, NV, t] = 0
      D[s, NV, t] = 0; E[s, NV, t] = 0; G[s, NV, t] = 0
      
      A[s, v, 1] = 0; B[s, v, 1] = 0; C[s, v, 1] = 0
      D[s, v, 1] = 0; E[s, v, 1] = 0; G[s, v, 1] = 0
    }
  }
}

# Computing Value of options in the grid
for(t in 2:(NT+1)) {
  for(s in 1:NS) {
    for(v in 1:(NV-1)) {
      price.array[1, v, t] = K
      price.array[NS, v, t] = 0
    }
  }
  for(l in 1:NS) {
    price.array[l, NV, t] = max(0, K - s.vec[l])
  }
  for(i in 2:(NS-1)) {
    price.array[i,1,t] = price.array[i,1,t-1]*(1 - r*dt - kappa*theta*dt/dv)
    + dt*0.5*r*s.vec[i]*(price.array[i+1,1,t-1] - price.array[i-1,1,t-1])/ds +
      kappa*theta*price.array[i,2,t-1]*dt/dv
  }
  for(j in 2:(NS-1)) {
    for(k in 2:(NV-1)) {
      A[j,k,t] = (1 - dt*(j-1)^2*(k-1)*dv - sig^2*(k-1)*dt/dv - r*dt)
      B[j,k,t] = (0.5*dt*(j-1)^2*(k-1)*dv - 0.5*dt*r*(j-1))
      C[j,k,t] = (0.5*dt*(j-1)^2*(k-1)*dv + 0.5*dt*r*(j-1))
      D[j,k,t] = (0.5*dt*sig^2*(k-1)/dv - 0.5*dt*kappa*(theta-(k-1)*dv)/dv)
      E[j,k,t] = (0.5*dt*sig^2*(k-1)/dv + 0.5*dt*kappa*(theta-(k-1)*dv)/dv)
      G[j,k,t] = 0.25*dt*sig*(j-1)*(k-1)
      price.array[j,k,t] = A[j,k,t]*price.array[j,k,t-1] + B[j,k,t]*price.array[j-1,k,t-1] +
        C[j,k,t]*price.array[j+1,k,t-1] + D[j,k,t]*price.array[j,k-1,t-1] + 
        E[j,k,t]*price.array[j,k+1,t-1] +
        G[j,k,t]*( price.array[j+1,k+1,t-1]+price.array[j-1,k-1,t-1]-
              price.array[j-1,k+1,t-1]-price.array[j+1,k-1,t-1] )
    }
  }
}

# Using information obtained from the grid, use interpolation to compute value of the put option
interp2(sig.vec, s.vec, as.matrix(price.array[,,2001]), sig , s0, method = "linear")
```
So, the value of the put option is 16.27 USD.
